Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-14 manuscript.tex
Figure replicating_MainenSejnowski1995

@@

\caption{The timing of the spikes produced following the repetition of a step stimuli is less reproducible than that to a noisy stimulus. The stimulus is shown in the top row, while trial repetitions of a simulated Leaky Integrate-and-Fire neuron are shown in the second row (with membrane potential represented by  dark blue color when light yellow colors when depolarized). While this seems paradoxical at first sight, this is due to the use of the same \emph{frozen} noise at each repetition and highlight the highly reproducible pattern of spikes when it is driven by a highly dynamic input. See this \href{https://github.com/laurentperrinet/2022_UE-neurosciences-computationnelles/blob/master/C_MainenSejnowski1995.ipynb}{notebook} for a replication of this result using a simple LIF model.}\label{fig:mainen}

>>>>

% C_MainenSejnowski1995_Perrinet.ipynb

@@

\caption{The timing of the spikes produced following the repetition of a step stimuli is less reproducible than that to a noisy stimulus. The stimulus is shown in the top row, while trial repetitions of a simulated Leaky Integrate-and-Fire neuron are shown in the second row (with membrane potential represented by dark blue color when light yellow colors when depolarized) and quantified by the average firing rate across trials (lower row). While this seems paradoxical at first sight, this is due to the use of the same \emph{frozen} noise at each repetition and highlight the highly reproducible pattern of spikes when it is driven by a highly dynamic input. See this~\href{https://github.com/laurentperrinet/2022_UE-neurosciences-computationnelles/blob/master/C_MainenSejnowski1995_Perrinet.ipynb}{notebook} for a replication of this result using a simple LIF model.}\label{fig:mainen}
